%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Author:
% Rohit Dhas (http://rohitdhas.dev)
%
% Original repository:
% https://github.com/rohitdhas/resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Rohit}{Dhas}{
\href{mailto:rohitdhas666@gmail.com}{rohitdhas666@gmail.com} | +91 9359952174
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Savitribai Phule, Pune \\ University}
\descript{Bachelor's in Computer Application}
\location{May 2023 | Ahemadnagar, IN}
\sectionsep

\subsection{NDV High School}
\descript{HSC (12th)}
\location{March 2020 | Beed, IN}
\location{ Percentage: 78 / 100}
\descript{SSC (10th)}
\location{March 2018 | Beed, IN}
\location{ Percentage: 89 / 100}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/rohitdhas}{\bf rohitdhas} \\
LinkedIn://  \href{https://www.linkedin.com/in/rohitdhas}{\bf rohitdhas} \\
Twitter://  \href{https://twitter.com/rohitdhas_dev}{\bf @rohitdhas\_dev} \\
Portfolio://  \href{https://rohitdhas.dev}{\bf rohitdhas.dev} \\
HackerRank:// \href{https://www.hackerrank.com/rohitdhas?hr_r=1}{\bf rohitdhas} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Database Management System \\
Software Engineering \\
Data Structures \& Algorithms \\
Operating System \\
Cloud Computing \\
Data Mining \\
Machine Learning \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\textbullet{} JavaScript \\ \textbullet{}  TypeScript \\ \textbullet{} Python \\ \textbullet{} C++ \\ \textbullet{} HTML/CSS \\ \textbullet{} MongoDB \\ \textbullet{} MySQL \\ \textbullet{} React JS \\ \textbullet{} Next JS \\ \textbullet{} Express JS \\ \textbullet{} Node JS \\ \textbullet{} AWS \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{QuadB Technologies}
\descript{| React JS Intern }
\location{Nov 2021 – Mar 2022 | Remote}
\vspace{\topsep}
\begin{tightemize}
\item Worked on Quadb's CRM project, which is a web based sales CRM.
\item Worked on insights feature of CRM which helps analyze patterns and optimize your workflow with the help of charts.
\item Tested and Debugged Source Code for better application
performance with a team of 3 individuals.
\item Tech:- React JS, Redux
\end{tightemize}
\sectionsep

\runsubsection{Parceldeck}
\descript{| Full Stack Development Intern }
\location{Apr 2022 - Sept 2022 | Remote}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Automated manual task of paying monthly COD remittances to users, by integrating Razorpay X API
\item Built a Simple Ticket System (in which users can explain their query and add some attachments) to allow users raise a ticket for their queries. 
% \item Built an API to upload and access product images to AWS S3
\item Implemented Sendgrid Dynamic Template service to send emails to users on different events.
\item Developed multiple REST APIs for tracking package details, creating new orders, managing weight discrepancies, etc.
% \item Built Cron Jobs for automating stuff like, updating shipment tracking status,  updating failed payments, etc.
\item Built reusable UI components using AntD and did API integration to display data in tabular form.
\item Tech:- React JS, Antd, Redux, Nest JS, MongoDB, AWS
\end{tightemize}
\sectionsep

\runsubsection{Taxadda}
\descript{| Backend Developer Intern}
\location{Sept 2022 – Dec 2022 | Remote}
\begin{tightemize}
\item Worked with exceljs lib to generate and validate dynamic bulk upload sheets.
\item Implemented search auto-complete in an API using mongodb altas search.
\item Wrote complex database queries using MongoDB aggregation operator to access, modify and manage data in DB.
% \item Implemented data (email \& phone) encryption for securing user data.
\item Debugged source code and optimised performance bottlenecks in backend system to improve app performance.
\item Tech:- Node JS, Express JS, MongoDB, Excel JS
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Code Box}
\descript{}
\location{}
\begin{tightemize}
\item Code Box is development platform where anyone can build websites using HTML, CSS and JS and show off their work online.
\item Tech Stack - React, Next JS, Tailwind CSS, MongoDB
\item Link - \href{https://code-box.vercel.app} {\bf code-box.vercel.app}
\end{tightemize} 
\sectionsep

\runsubsection{StoreFront}
\descript{}
\location{}
\begin{tightemize}
\item Storefront is a E-Commerce app for buying electronic stuff.
\item Tech Stack - React (TypeScript), Redux Toolkit, Prime React + Tailwind CSS, Next JS, MongoDB, AWS EC2 , Stripe API, Next Auth, GraphQL + Apollo Server
\item Link - \href{https://storefront.rohitdhas.dev} {\bf storefront.rohitdhas.dev}
\end{tightemize} 
\sectionsep

\runsubsection{TopStore REST API}
\descript{}
\location{}
\begin{tightemize}
\item It's a free REST API that provides dummy product data.
\item Tech Stack - Node JS, Express, MongoDB
\item Link - \href{https://topstore-api.herokuapp.com} {\bf topstore-api.herokuapp.com}
\end{tightemize} 
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
